Ordinal bhsdtr tutorial

### 2020-02-17 ordinal/Readme.Rmd
a note on free parameters

It is only at this layer of abstraction that a mechanism becomes a
*psychological* mechanism. It is my belief that it may be possible to
formalize the process of inference at this level of abstraction. If
such a formal theory of psychological inference was to be discovered,
it would perhaps resemble an abstract theory of agents, tasks, and
cognitive functions. Rational analysis (J.R. Anderson) and
probabilistic models of cognition (Chater, Oaksford, Tenenbaum,
Griffiths, etc) seem to be promising starting points, as does the
Reinforcement Learning framework (Sutton and Barto) in which, to my
knowledge, the first promising weak (a good thing), formal definition
of purposeful action (i.e., of behavior) was proposed, inspired by the
writings of Tolman and Perry.

>>>>

It is only at this layer of abstraction that a mechanism becomes a
*psychological* mechanism. It is my belief that it may be possible to
formalize the process of inference at this level of abstraction. If
such a formal theory of psychological inference was to be discovered,
it would perhaps resemble an abstract theory of agents, tasks, and
cognitive functions. Rational analysis (J.R. Anderson) and
probabilistic models of cognition (Chater, Oaksford, Tenenbaum,
Griffiths, etc) seem to be promising starting points, as does the
Reinforcement Learning framework (Sutton and Barto) in which, to my
knowledge, the first promising weak (a good thing), formal definition
of purposeful action (i.e., of behavior) was proposed, inspired by the
writings of Tolman and Perry. There were times when saw that the
number of free parameters prevents us from answering certain valid and
important questions. By identifying the limits of optimal purposeful
action, this kind of analysis may sometimes significantly lower the
number of free parameters in the models of psychological processes.
